R Notebook

### 2021-05-28 FEM_R/ELSA_data_check.Rmd
Lots of little changes for ROC validation, couple of R scripts focused on calculating DFLYs

@@

>>>>

rm(cancre, diabe, lunge, smoken, smokev, smokef, drink)

@@

# Now get the proportion of missing data in variables in raw stock file
stock <- read_dta('ELSA_stock_preImpute.dta')

pMiss(stock$age)
pMiss(stock$male)
pMiss(stock$bmi)
pMiss(stock$logbmi)
pMiss(stock$smoken)
pMiss(stock$smokev)
pMiss(stock$educ)

print('-----------')

pMiss(stock$cancre)
pMiss(stock$diabe)
pMiss(stock$hearte)
pMiss(stock$stroke)
pMiss(stock$lunge)
pMiss(stock$hibpe)

### 2021-05-28 FEM_R/calculate_dflys_from_summary.Rmd
Lots of little changes for ROC validation, couple of R scripts focused on calculating DFLYs

# Cohort disease life years
diseaseVarLifeyear(c, 'cancre')
diseaseVarLifeyear(c, 'diabe')
diseaseVarLifeyear(c, 'hearte')
diseaseVarLifeyear(c, 'lunge')
diseaseVarLifeyear(c, 'hibpe')
diseaseVarLifeyear(c, 'stroke')
diseaseVarLifeyear(c, 'alzhe')
diseaseVarLifeyear(c, 'demene')
diseaseVarLifeyear(c, 'smoken')
diseaseVarLifeyear(c, 'drink')
diseaseVarLifeyear(c, 'heavy_smoker')
diseaseVarLifeyear(c, 'problem_drinker')
```

@@

disabilityLifeYearComp <- function(c, i, int.name) {

  c.avg.dis <- disabilityLifeYearsCohort(c)

  i.avg.dis <- disabilityLifeYearsCohort(i)

  print(int.name)
  print(paste('Cohort Average Lifeyears:        ', signif(c.avg.dis, digits=4)))
  print(paste('Intervention Average Lifeyears:  ', signif(i.avg.dis, digits=4)))
  print(paste('Increase:                        ', signif(x = (i.avg.dis - c.avg.dis), digits=4)))
}

disabilityFreeLifeYearsCohort <- function(c) {
  total_disfree <- c$a_not_disabled_all * c$m_endpop_all
  sum_tot_disfree <- sum(total_disfree)
  avg_disfree <- sum_tot_disfree / c$m_endpop_all[1]
  return(avg_disfree)
}
```

### Cohort
```{r}
# Cohort life years
c <- cohort
c.dly <- disabilityLifeYearsCohort(c)
print(paste0('Cohort Disabled Life Years: ', signif(c.dly, digits=4)))
print('-------------------')
c.dfly <- disabilityFreeLifeYearsCohort(c)
print(paste0('Cohort Disability Free Life Years: ', signif(c.dfly, digits=4)))

# Cohort disease life years
#diseaseVarLifeyear(c, 'cancre')
#diseaseVarLifeyear(c, 'diabe')
#diseaseVarLifeyear(c, 'hearte')
#diseaseVarLifeyear(c, 'lunge')
#diseaseVarLifeyear(c, 'hibpe')
#diseaseVarLifeyear(c, 'stroke')
#diseaseVarLifeyear(c, 'alzhe')
#diseaseVarLifeyear(c, 'demene')
#diseaseVarLifeyear(c, 'smoken')
#diseaseVarLifeyear(c, 'drink')
#diseaseVarLifeyear(c, 'heavy_smoker')
#diseaseVarLifeyear(c, 'problem_drinker')
```

@@

total_dflys_s <- s$a_disabled_all * s$m_endpop_all
sum_tot_dflys_s <- sum(total_dflys_s)
avg_dflys_s <- sum_tot_dflys_s / s$m_endpop_all[1]

avg_dflys
avg_dflys_s

@@

```{r}

c <- cohort

total_dflys <- c$a_disabled_all * c$m_endpop_all
sum_tot_dflys <- sum(total_dflys)
avg_dflys <- sum_tot_dflys / c$m_endpop_all[1]

# No Heart Disease
h <- heart_c

total_dflys_h <- h$a_disabled_all * h$m_endpop_all
sum_tot_dflys_h <- sum(total_dflys_h)
avg_dflys_h <- sum_tot_dflys_h / h$m_endpop_all[1]

avg_dflys
avg_dflys_h

### Not Disabled
```{r}

disabilityFreeComparison <- function(c, i, int.name) {
  tot.df <- c$a_not_disabled_all * c$m_endpop_all
  sum.tot.df <- sum(tot.df)
  avg.df <- sum.tot.df / c$m_endpop_all[1]

  tot.df.i <- i$a_not_disabled_all * i$m_endpop_all
  sum.tot.df.i <- sum(tot.df.i)
  avg.df.i <- sum.tot.df.i / i$m_endpop_all[1]

  print(int.name)
  print(paste('Cohort Average Disability Free:', signif(avg.df, digits=4)))
  print(paste('Intervention Disability Free:', signif(avg.df.i, digits=4)))
  print(paste('Difference:', signif(x = (avg.df.i - avg.df), digits=4)))
}

c <- cohort
# No Heart Disease
h <- heart_c

disabilityFreeComparison(c, h, 'No Heart Disease')

>>>>

# Cohort disease life years
diseaseVarLifeyear(c, 'cancre')
diseaseVarLifeyear(c, 'diabe')
diseaseVarLifeyear(c, 'hearte')
diseaseVarLifeyear(c, 'lunge')
diseaseVarLifeyear(c, 'hibpe')
diseaseVarLifeyear(c, 'stroke')
diseaseVarLifeyear(c, 'alzhe')
diseaseVarLifeyear(c, 'demene')
#diseaseVarLifeyear(c, 'smoken')
#diseaseVarLifeyear(c, 'drink')
#diseaseVarLifeyear(c, 'heavy_smoker')
#diseaseVarLifeyear(c, 'problem_drinker')
```

@@

disabilityLifeYearComp <- function(c, i, int.name) {
  c.avg.dis <- disabilityLifeYearsCohort(c)
  i.avg.dis <- disabilityLifeYearsCohort(i)
  print(int.name)
  print(paste('Cohort Average Lifeyears:        ', signif(c.avg.dis, digits=4)))
  print(paste('Intervention Average Lifeyears:  ', signif(i.avg.dis, digits=4)))
  print(paste('Increase:                        ', signif(x = (i.avg.dis - c.avg.dis), digits=4)))
}

disabilityFreeLifeYearsCohort <- function(c) {
  total_disfree <- c$a_not_disabled_all * c$m_endpop_all
  sum_tot_disfree <- sum(total_disfree)
  avg_disfree <- sum_tot_disfree / c$m_endpop_all[1]
  return(avg_disfree)
}

disabilityFreeLifeYearsComp <- function(c, i, int.name) {
  c.avg.dis <- disabilityFreeLifeYearsCohort(c)
  i.avg.dis <- disabilityFreeLifeYearsCohort(i)
  print(int.name)
  print(paste('Cohort Average Disability Free Lifeyears:        ', signif(c.avg.dis, digits=4)))
  print(paste('Intervention Average Disability Free Lifeyears:  ', signif(i.avg.dis, digits=4)))
  print(paste('Increase:                                        ', signif(x = (i.avg.dis - c.avg.dis), digits=4)))
}

disVarDFLY <- function(c, var) {
  prevVar <- paste0('p_', var, '_all')

  c.tot.var.dfly <- c[prevVar] * c$a_not_disabled_all * c$m_endpop_all
  c.sum.var.dfly <- sum(c.tot.var.dfly)
  c.avg.var.dfly <- c.sum.var.dfly / c$m_endpop_all[1]

  print(paste0(var, ':    ', signif(c.avg.var.dfly, digits=4)))
}
```

### Cohort
```{r}
# Cohort life years
c <- cohort
c.dly <- disabilityLifeYearsCohort(c)
print(paste0('Cohort Disabled Life Years: ', signif(c.dly, digits=4)))
print('-------------------')
c.dfly <- disabilityFreeLifeYearsCohort(c)
print(paste0('Cohort Disability Free Life Years: ', signif(c.dfly, digits=4)))
print('-------------------')

# Cohort disability life years
disVarDFLY(c, 'cancre')
disVarDFLY(c, 'diabe')
disVarDFLY(c, 'hearte')
disVarDFLY(c, 'lunge')
disVarDFLY(c, 'hibpe')
disVarDFLY(c, 'stroke')
disVarDFLY(c, 'alzhe')
disVarDFLY(c, 'demene')
#disVarDFLY(c, 'smoken')
#disVarDFLY(c, 'drink')
#disVarDFLY(c, 'heavy_smoker')
#disVarDFLY(c, 'problem_drinker')
```

@@

disabilityFreeLifeYearsComp(c, s, 'No Smoking')
```

@@

```{r}
c <- cohort
# No Heart Disease
h <- heart_c
disabilityFreeLifeYearsComp(c, h, 'No Heart Disease')
cohortLifeyear(c)
```

### Not Disabled
```{r}
c <- cohort
# No Heart Disease
h <- heart_c

disabilityFreeLifeYearsComp(c, h, 'No Heart Disease')
```
